Fisher Information based Disambiguation of Human Intent - An Experimental Evaluation

### 2018-01-05 NewTexFile/GopinathArgall_RSS2018.tex
Commit from laptop

\begin{abstract}
The abstract goes here.
\end{abstract}

@@

\section{Introduction}
This demo file is intended to serve as a ``starter file" for the
Robotics: Science and Systems conference papers produced under \LaTeX\
using IEEEtran.cls version 1.7a and later.

@@

Section text here.

\section{Mathematical Formalism}
\subsection{Disambiguation Schemes}
\subsubsection{Fisher Information Based Metric}
\subsubsection{Entropy-based Metric}
\subsubsection{Heuristic-based Metric}

\subsection{Intent inference}
\subsubsection{Dynamic Field Theory Based}
\subsubsection{Bayesian Inference}
\subsubsection{Confidence Functions}

@@

\section{RSS citations}

Please make sure to include \verb!natbib.sty! and to use the
\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
citation commands, most usefully \verb!\citet!. For example, rather than the
awkward construction

{\small
\begin{verbatim}
\cite{kalman1960new} demonstrated...
\end{verbatim}
}

\noindent
rendered as ``\cite{kalman1960new} demonstrated...,''
or the
inconvenient

{\small
\begin{verbatim}
Kalman \cite{kalman1960new} 
demonstrated...
\end{verbatim}
}

\noindent
rendered as 
``Kalman \cite{kalman1960new} demonstrated...'', 
one can
write

{\small
\begin{verbatim}
\citet{kalman1960new} demonstrated... 
\end{verbatim}
}
\noindent
which renders as ``\citet{kalman1960new} demonstrated...'' and is 
both easy to write and much easier to read.

\subsection{RSS Hyperlinks}

This year, we would like to use the ability of PDF viewers to interpret
hyperlinks, specifically to allow each reference in the bibliography to be a
link to an online version of the reference. 
As an example, if you were to cite ``Passive Dynamic Walking''
\cite{McGeer01041990}, the entry in the bibtex would read:

{\small
\begin{verbatim}
@article{McGeer01041990,
  author = {McGeer, Tad}, 
  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}}, 
  volume = {9}, 
  number = {2}, 
  pages = {62-82}, 
  year = {1990}, 
  doi = {10.1177/027836499000900206}, 
  URL = {http://ijr.sagepub.com/content/9/2/62.abstract}, 
  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html}, 
  journal = {The International Journal of Robotics Research}
}
\end{verbatim}
}
\noindent
and the entry in the compiled PDF would look like:

\def\tmplabel#1{[#1]}

\begin{enumerate}
\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
1990.
\end{enumerate}
%
where the title of the article is a link that takes you to the article on IJRR's website.

Linking cited articles will not always be possible, especially for
older articles. There are also often several versions of papers
online: authors are free to decide what to use as the link destination
yet we strongly encourage to link to archival or publisher sites
(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
the extent possible.

\section{Conclusion} 
\label{sec:conclusion}

The conclusion goes here.

>>>>

\begin{abstract}
In this paper, we treat the problem of intent disambiguation in terms of information theoretic principles. The effectiveness of assistive robots is closely related to their ability to infer the users' needs and intentions and provide appropriate types of assistance quickly, confidently and accurately.  We propose two different control mode selection schemes for intent disambiguation using notions of entropy and Fisher information in the context of assistive robotic manipulation. The proposed algorithms characterize the disambiguation capabilities of different control modes by the forward projection of probability distributions over goals and computing the relevant information theoretic measures. Our previous exploratory pilot studies revealed that the success of the disambiguation system depends on a variety of factors and choice of parameters. In order to thoroughly investigate the impact of the choice of various parameters and components, we present extensive simulation results both for point-robots that reside in different spaces as well as on the simulated robotic arm. Our results indicate that with the disambiguation algorithm the robot is able to assist earlier during task execution. Furthermore, the goal inferences are more accurate when operating in the disambiguating modes. 
\end{abstract}

@@

\section{Introduction}
Assistive shared-control machines such as robotic arms and myoelectric prosthesis have the potential to transform the lives of millions of people with motor impairments as a result of spinal cord injuries or brain traumas. These machines can promote independence, enhance the quality of lives and revolutionize the way they interact with society. These machines help to extend the mobility and manipulation capabilities of individuals thereby helping them perform activities of daily living in a more effective manner.

The efficacy of assistive machines rely on their ability to infer the users' needs and intentions and is often a bottleneck for providing appropriate assistance quickly, confidently and accurately. Due to the dimensionality mismatch between the high-dimensional robots and the low-dimensional interfaces, the users' are typically constrained to produce control commands that do not reveal the intent more expressively. Therefore, intent inference is a necessary and crucial component to ensure appropriate assistance. Specifically, in assistive robotic manipulation, often the first step of a task is to reach for and grasp discrete objects in the environment. Therefore in this context, intent inference can be cast as a problem of maintaining the probability distribution over all possible discrete goals (objects) in the workspace.

Our insight is that the information contained in control command issued in certain control modes is more useful for accurate inference and thereby will help the robot in providing the appropriate kind of assistance. In this work, we rely on information theoretic principles to quantify the information regarding intent disambiguation contained in different control modes and select control modes that maximize intent disambiguation.

@@

\section{Mathematical Formalism}
\subsection{Set Theoretic Treatment of Control Modes}
\subsection{Disambiguation Schemes}
\subsubsection{Fisher Information Based Metric}
\subsubsection{Entropy-based Metric}
\subsubsection{Heuristic-based Metric}

\subsection{Intent inference}
\subsubsection{Dynamic Field Theory}
\subsubsection{Bayesian Inference}
\subsubsection{Confidence Functions}

@@

\section{Results}
\section{Discussion}
\section{Conclusion}
\section{References}
